Title

### 2024-06-22 paper/main.tex
Updates

Any two variables in a DAG that do not have an edge between them imply a
conditional independence test that is they are independent given the parents of
both the variables, $ X \ci Y | pa(X) \cup pa(Y) $. In the case of model
testing, a CI statement like this can be used to check whether the assumption
of the model holds in the data or is violated. For mixed data, a few different
CI tests have been proposed such as likelihood-ratio based, and residualization
based. However, if we just use the CI test to check the p-value we cannot use
it to find the modification that is able to improve the score the most.

The idea behind using the measure of association for modifying DAGs is that,
for any given model and a dataset, we can use the condtiional measure of
association to compute the amount of correlation in the data that is still not
explained by the model. Based on this, we can compute how much improvement in
the explanation would happen if we were to add an edge between variables. This
can then be ranked using the maximum improvement. Give some examples here.

>>>>

Any two variables in a DAG that do not have an edge between them imply a
conditional independence test that is they are independent given the parents of
both the variables, $ X \ci Y | pa(X) \cup pa(Y) $. In the case of model
testing, a CI statement like this can be used to check whether the assumption
of the model holds in the data or is violated. For mixed data, a few different
CI tests have been proposed such as likelihood-ratio based, and residualization
based. However, if we just use the CI test to check the p-value we cannot use
it to find the modification that is able to improve the score the most. We can
however use the measure of association to check which assocation between the
variables in the data is not explained by the model. Using this the expert can
decide to add an edge between the variables but will need to choose the
direction of the edge.

The idea behind using the measure of association for modifying DAGs is inspired
by modification indices in SEM. For any given model and a dataset, we can use
the condtiional measure of association to compute the amount of correlation in
the data that is still not explained by the model. Based on this, we can
compute how much improvement in the explanation would happen if we were to add
an edge between variables. This can then be ranked using the maximum
improvement. Give some examples here.
